%-------------------------
% Resume in Latex
% Author: Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{vntex}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/SeenSeens}{\Large Truong Dinh Tuan }} & Email : \href{mailto:tuantruong829@gmail.com}{tuantruong829@gmail.com}\\
  \href{https://github.com/SeenSeens}{https://github.com/SeenSeens} & Linkedin : \href{https://www.linkedin.com/in/tuanseenit}{https://www.linkedin.com/in/tuanseenit}\\ & Mobile : 0385-573-558 - 0968-320-572
\end{tabular*}

%-----------Introduce-----------------

%-----------career goals-----------------
  

  
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {TBAY Technology Services Limited Liability Company}{Ho Chi Minh City}
      {Freelancer}{08/2024 - Present}
      \resumeItemListStart
        \item {Developing, maintaining, and upgrading WordPress websites, ensuring clean code, ease of maintenance, and adherence to programming standards.}
        \item {Developing custom plugins as per requirements.}
        \item {Optimizing performance and security for websites, ensuring fast page load times and a good user experience.}
        \item {Providing support and guidance to internship students.}
      \resumeItemListEnd
    \resumeSubheading
      {Halink Trading and Service Limited Liability Company}{Ho Chi Minh City}
      {Laravel \& Vue Developer}{04/2024 - 07/2024}
      \resumeItemListStart
        \item {Developing and maintaining web applications using Laravel, ensuring clean code, ease of maintenance, and adherence to programming standards.}
        \item {Designing databases and managing data efficiently using Laravel's Eloquent ORM, ensuring data integrity and system performance.}
        \item {Building and deploying RESTful APIs to provide data for the frontend, ensuring stable operation and security of the APIs.}
        \item {Optimizing performance and security for web applications, ensuring fast page load times and a good user experience.}
        \item {Assisting in deploying web applications on LEMP servers, configuring Nginx, and setting up SSL certificates to ensure secure network communication.}
        \item {Researching and applying Tailwind CSS, VueJS, and Livewire in real-world projects to enhance user interfaces and work efficiency.}
        \item {Participating in project management and teamwork, utilizing Agile methodologies and tools like Jira to track progress and collaborate with colleagues.}
      \resumeItemListEnd

    \resumeSubheading
      {Halink Trading and Service Limited Liability Company}{Ho Chi Minh City}
      {WordPress Develeper}{04/2019 - 02/2020}
      \resumeItemListStart
        \item {Designing and developing WordPress websites, participating in the entire process from ideation and interface design to development and deployment.}
        \item {Performing maintenance and upgrades for WordPress websites, adjusting and enhancing features to meet business requirements and improve user experience.}
        \item {Developing and integrating new features such as payment systems, login functionality, and content management to enhance website functionality.}
        \item {Maintaining and debugging websites to ensure performance and security, performing software updates and routine maintenance.}
        \item {Resolving technical issues related to WordPress, ensuring website performance and security.}
      \resumeItemListEnd
      \resumeSubheading
        {Applancer JSC}{Ho Chi Minh City}
        {PHP Intern - Yii2.}{10/2018 - 12/2018}
      \resumeItemListStart
        \item {PHP Intern - Yii2.}
      \resumeItemListEnd
      \resumeSubheading
      {Dat Viet Software Company} {Ho Chi Minh City}
      {C\# Intern - WPF} {05/2018 - 07/2018}
      \resumeItemListStart
        \item {C\# Intern - WPF.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh City University of Information Technology}{Ho Chi Minh City}
      {Information Technology}{08/2022 - 2024}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeItem{Languages}{PHP, JavaScript, Python}
   \resumeItem{Database}{MSSQL, MySQL, MongoDB}
   \resumeItem{Framework}{WordPress, Laravel, ExpressJs, Flask}
 \resumeSubHeadingListEnd

%--------ACTIVATE SKILLS------------
\section{Activities}
 \resumeSubHeadingListStart
   \resumeItem{Scientific Research}{}
   \resumeItem{Solana Consumer Hack \#04}{}
   \resumeItem{ITC Programming Club}{}
   \resumeItem{Student Association}{}
   \resumeItem{Youth Union}{}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
