%-------------------------
% Resume in Latex
% Author: Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/SeenSeens}{\Large Truong Dinh Tuan}} & Email : \href{mailto:truongtuan829@gmail.com}{truongtuan829@gmail.com}\\
  \href{https://github.com/SeenSeens}{https://github.com/SeenSeens} & Mobile : 0385-573-558 \\
\end{tabular*}

%-----------Introduce-----------------
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Colleges Information Technology City. Ho Chi Minh}{}
      {Information technology}{Aug. 2022 -- Dec. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Halink Trading and Services Limited Liability Company}{Ho Chi Minh City}
      {Laravel \& Vue Intern}{Apr 2024 - Present}
      \resumeItemListStart
        \resumeItem{Development and maintenance of web applications using Laravel}{Participate in web application development projects using Laravel, ensuring the source code is clean, easy to maintain, and compliant with programming standards.}
        \resumeItem{Database design and data management with Laravel's Eloquent ORM}{Efficient database design and data management using Laravel's Eloquent ORM, ensuring system integrity and performance.}
        \resumeItem{Build and deploy RESTful APIs to provide data to the frontend.}{Create and manage RESTful APIs to provide data to the frontend, ensuring the APIs operate stably and securely.}
        \resumeItem{Optimize performance and security for web applications.}{Optimize the performance of web applications, ensuring fast page load times and good user experience. Implement security measures to protect user and application data.}
        \resumeItem{Support deploying web applications to LEMP server, configuring Nginx and setting up SSL certificates.}{Support deploying web applications to LEMP servers, configuring Nginx and setting up SSL certificates to ensure secure network communication.}
        \resumeItem{Tailwind CSS}{Research and apply Tailwind CSS to projects, helping to improve user interface and working performance.}
        \resumeItem{VueJS}{Learn about VueJS and how to use it in web application development, practice building components, and interacting with the backend.}
        \resumeItem{Laravel}{Master the Laravel framework, from installation to developing complete web applications, applying knowledge to real projects.}
        \resumeItem{Livewire Laravel}{Learn and apply Livewire to build highly interactive web applications without pure JavaScript.}\resumeItem{Bento Grid project}{Apply knowledge of Tailwind CSS and VueJS to build project interfaces and functionality, project quality and progress.}
        \resumeItem{The project uses Laravel and Livewire}{Participate in developing project features, working with team members to ensure seamless integration between parts of the application.}
        \resumeItem{Project management and teamwork}{Learn and apply Agile project management methods, using tools like Jira to track progress and coordinate with colleagues.Participate in regular meetings, discuss and contribute ideas to improve the project.}
      \resumeItemListEnd

    \resumeSubheading
      {Halink Trading and Services Limited Liability Company}{Ho Chi Minh City}
      {WordPress Develeper}{Apr 2019 - Feb 2020}
      \resumeItemListStart
        \resumeItem{Design and development WordPress websites}{Participate in the entire process from idea generation, interface design to developing and deploying new websites on the WordPress platform}
        \resumeItem {Perform maintenance and upgrades of current WordPress websites}{Adjust and enhance features of existing websites to meet business requirements and improve user experience.}
        \resumeItem {Add new features and integrate with third-party services}{Develop and integrate new features such as payment systems, login, and content management to enhance website functionality.}
        \resumeItem {Maintain and debug the website to ensure performance and security}{Ensure websites operate stably and securely through software updates, patches, and periodic maintenance.}
        \resumeItem {Resolve technical issues related to WordPress}{Fix technical issues related to WordPress, ensure performance and security of websites.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeItem{Languages}{PHP, JavaScript, Python}
   \resumeItem{Database}{MSSQL, MySQL, MongoDB}
   \resumeItem{Framework}{WordPress, Laravel, Express, Vue, Flask}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
